Reproduction of Civic Honesty around the Globe

### 2021-03-23 outputs/paper/paper.Rmd
Update paper.Rmd

>>>>

## Methodology and Data Collection
The research team visited 355 cities in 40 countries and dropped a total of 17,303 wallets between July 2013 and December 2016 [@citeCohn]. The target sample size was set at 400 per country except for the US, UK and Poland: the sample size for these three countries is greater than 400 since two additional treatment conditions (BigMoney and Money-NoKey conditions) are included [@citeCohn]. The dataset contains not just where and when the wallets were dropped and reported but also situational factors that may affect the response of the experiment, such as whether there was a computer at the recipient’s desk, how many witnesses or coworkers were there when the wallet was handed over to the recipient, or whether a security camera was visible at the recipient’s desk [@citeCohn].

These situational factors were recorded by research assistants, and some of the factors highly rely on their individual judgment. For example, the ‘Busyness’ category, which is measured on a 7-point scale from “not at all” (0) to “very busy”, and the ‘Friendliness’ category, which is measured on a 7-point scale from “very unfriendly” (0) to “very friendly” (6), were graded by the assistants according to their estimation and judgment since they had to measure actions and behaviors which are intangible unlike a computer or security camera [@citeCohn].

In addition, the estimation of the assistants can be incorrect, and eventually they might record false information during the data collection process. For example, in terms of the ‘Recipient age’ category, the assistants had to guess the recipient’s age and select one from six options: < 20, 20-30, 30-40, 40-50, 50-60, and > 60. What if the recipient looks 30? The assistants might choose either 20-30 or 30-40 based on their judgement since it is a huge challenge to correctly guess someone's age by looking at his or her face. A research team from the Department of Computer Science and Engineering at Michigan State University studied the ability of humans to estimate age using face images collected from crowdsourcing and found that the accuracy of guessing the age correctly with a margin of error of plus/minus 5 years is between 50% and 70% [@citeAgeEstimation]. Namely, there are high chances that the assistants might have recorded inaccurate information for some of those variables that require the researcher's estimation. As a consequence, this can lead to distorted results of the analysis.

The selection of countries raises another issue of the dataset: Do those countries really represent the globe? 40 countries are selected and examined for the research, and almost half (19 countries) of them are European countries. However, in reality, the population of all European countries is approximately 10% of the world's population [@citeWorldContinents]. In terms of the number of countries, there are merely 44 countries in Europe, out of 195 countries in the world, which accounts for about one-fourth of the total countries [@citeCountriesEurope]. Is it because those unselected countries could not meet the requirements of selection criteria? The selection criteria requirements for the country category are as follows:

* The country must have a sufficient number (at least 100,000) of large cities;
* The country must have a plenty of “feasible drop-off locations” where can be easily accessible;
* The country must be “easy to visit and safe enough” for research assistants to proceed with the wallet dropping experiment; and
* The country must have less strict customs, immigration, and banking regulation [@citeCohn].

It can be arguable that UAE, Malaysia, and Kazakhstan were selected instead of other Asian countries with larger population size and more large cities such as Japan, Philippines, Vietnam, and South Korea [@citeCityPopulations]. Japan was not included in the category even though the country has the most and tenth-most populous cities in the world: Tokyo and Osaka [@citeCityPopulations]. Furthermore, Japan was one of the “10 Safest Countries In The World To Visit” chosen by Forbes in 2020; otherwise, none of the selected Asian countries was not included in the list [@citeSafestCountries].

The research data was collected by 13 research assistants: 11 male and 2 female born between 1985 and 1993. The assistants were instructed to say: “Hi, I found this [showing the wallet] on the street just around the corner” [@citeCohn]. After handing the wallet over to the recipient, they were also guided to say: “Somebody must have lost it. I’m in a hurry and have to go. Can you please take care of it?” [@citeCohn]. If the recipient contacts the email written on the business card inside the wallet to return it, the response variable is recorded as 1, meaning being responded. Even if the recipient makes a minor typo on the email address, the recipient email is designed to receive it unless misspelling the domain name [@citeCohn].
